\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-10-17 doc/flexiblesusy-paper.tex
Changed description of the two loop Higgs corrections in section 5 to match new plan which we agreed upon and Alex has implemented.  still need to fix later section.

\fs allows the user to add leading two-loop contributions to the CP-even Higgs
tadpoles and self-energies.  For MSSM-like models (with two CP-even
Higgs bosons, one CP-odd Higgs boson, one neutral Goldstone boson)
these corrections can be enabled by setting \code{UseHiggs2LoopMSSM =
  True} in the model file and by defining the effective $\mu$-term
\code{EffectiveMu = \\[Mu]}.  This will add the zero-momentum
corrections of the order $O(y_t^4 + y_b^2 y_t^2 + y_b^4)$, $O(y_t^2
g_3^2)$, $O(y_b^2 g_3^2)$, $O(y_\tau^4)$ from
\cite{Degrassi:2001yf,Brignole:2001jy,Dedes:2002dy,Brignole:2002bz,Dedes:2003km}.
For NMSSM-like models (with three CP-even Higgs bosons, two CP-odd
Higgs bosons, one neutral Goldstone boson) the two-loop contributions
are enabled by setting \code{UseHiggs2LoopNMSSM = True} and by
defining the effective $\mu$-term like \code{EffectiveMu = \\[Lambda]
  vS / Sqrt[2]}, for example.  This will add the zero-momentum
corrections of the order $O(y_t^2 g_3^2)$, $O(y_b^2 g_3^2)$ from
\cite{Degrassi:2009yq}.  If one also wishes to include the MSSM contributions of the order $O(y_\tau^4)$, $O(y_t^4 + y_t^2 y_b^2 + y_b^4)$ as well
\cite{Brignole:2001jy,Dedes:2003km} then one can also set both\footnote{Please note that with both of thse options set true it is the NMSSM corrections for $O(y_t^2 g_3^2)$, $O(y_b^2 g_3^2)$ which will be applied rather the the MSSM corrections for that order.} \code{UseHiggs2LoopMSSM = True} and \code{UseHiggs2LoopNMSSM = True}.

 In the case of the NMSSM the default option is to have both flags set
 to true as we feel that it is valuable to have these MSSM corrections
 for scenarios where there singlet mixing is very small and in
 particular for cross checks against the MSSM when close to the MSSM
 limit of the model.  However in cases where the singlet mixing is
 large the result at $O(y_t^4 + y_t^2 y_b^2 + y_b^4)$ and
 $O(y_\tau^4)$ will not be complete and including these corrections
 could in principle even make the numerical result further away from
 the correct two loop result at that order if there is a cancellation
 with the missing contributions.  So while including such partial
 two-loop corrections is does not change the formal accuracy the user
 should choose whether or not to include these corrections based on
 the physics they study.  Similarly in models that go beyond the NMSSM
 the user must decide based the physics whether on not these
 corrections will give the leading two-loop corrections in their
 model.

>>>>

\fs allows the user to add leading two-loop contributions to the
CP-even Higgs tadpoles and self-energies.  For MSSM-like models (with
two CP-even Higgs bosons, one CP-odd Higgs boson, one neutral
Goldstone boson) routines dor caluclating these corrections will be
generated by setting \code{UseHiggs2LoopMSSM = True} in the model file
and by defining the effective $\mu$-term \code{EffectiveMu = \\[Mu]}.
This will add the zero-momentum corrections of the order $O(y_t^4 +
y_b^2 y_t^2 + y_b^4)$, $O(y_t^2 g_3^2)$, $O(y_b^2 g_3^2)$,
$O(y_\tau^4)$ from
\cite{Degrassi:2001yf,Brignole:2001jy,Dedes:2002dy,Brignole:2002bz,Dedes:2003km}.
For NMSSM-like models (with three CP-even Higgs bosons, two CP-odd
Higgs bosons, one neutral Goldstone boson) the two-loop contributions
are generated by setting \code{UseHiggs2LoopNMSSM = True} and by
defining the effective $\mu$-term like \code{EffectiveMu = \\[Lambda]
  vS / Sqrt[2]}, for example.  This will add the zero-momentum
corrections of the order $O(y_t^2 g_3^2)$, $O(y_b^2 g_3^2)$ from
\cite{Degrassi:2009yq} and also the MSSM contributions of the order
$O(y_\tau^4)$, $O(y_t^4 + y_t^2 y_b^2 + y_b^4)$ as well
\cite{Brignole:2001jy,Dedes:2003km} which only represent a partial
correction for that order in the NMSSM, but can be a good approximation
when singlet mixing is very small.

 The corrections can then be used in the calculation of the Higgs
 masses, when appropriate settings are selected in the SLHA file. Note
 that even in the NMSSM the user miust make an important decision as
 to whether or not to enable the generated MSSM corrections which are
 incomplete in the NMSSM.  We feel that it is valuable to have
 these MSSM corrections for scenarios where there singlet mixing is
 very small and in particular for cross checks against the MSSM when
 close to the MSSM limit of the model.  However in cases where the
 singlet mixing is large the result at $O(y_t^4 + y_t^2 y_b^2 +
 y_b^4)$ and $O(y_\tau^4)$ will not be complete and including these
 corrections could in principle even make the numerical result further
 away from the correct two loop result at that order if there is a
 cancellation with the missing contributions.  So while including such
 partial two-loop corrections does not change the formal accuracy
 the user should choose whether or not to include these corrections
 based on the physics they study.  Similarly in models that go beyond
 the NMSSM the user must decide based the physics whether on not these
 corrections will give the leading two-loop corrections in their
 model.
